---
title: "title"
subtitle: "subtitle"
author: "author"
output:
  xaringan::moon_reader:
    css: ["default", "css/lexis.css", "css/lexis-fonts.css"]
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
      ratio: "16:9"
    seal: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
    warning = FALSE,
    message = FALSE,
    comment = "#>",
    fig.retina = 3 # Better figure resolution
)
today <- format(Sys.Date(), format="%B %d %Y")
```

```{r xaringan-tile-view, echo=FALSE}
# Enables the ability to show all slides in a tile overview by pressing "o"
# devtools::install_github("gadenbuie/xaringanExtra")
xaringanExtra::use_tile_view()
```

layout: true

<!-- this adds the link footer to all slides, depends on my-footer class in css-->

<div class="footer-small">
<span>
Footer text
</span>
</div>

---
name: title-slide
class: title-slide, center, middle, inverse

# Title

.large[First last]

Date: `r today`

---

# .center[Text styling]

.leftcol[
# Header level 1

## Header level 2

### Header level 3

#### Header level 4

##### Header level 5

###### Header level 6

]
.rightcol[
Regular

_Italics_

**Bold**

***Bold italics***

~~Strikethrough~~

.fancy[Fancy text]

[external link](https://github.com/jhelvy/lexis)<br>

`Inline code`
]

---
class: inverse

# .center[Inverse text styling]

.leftcol[
# Header level 1

## Header level 2

### Header level 3

#### Header level 4

##### Header level 5

###### Header level 6

]
.rightcol[
Regular

_Italics_

**Bold**

***Bold italics***

~~Strikethrough~~

.fancy[Fancy text]

[external link](https://github.com/jhelvy/lexis)<br>

`Inline code`
]

---

## .center[Colors!]

.leftcol40[
`.red[text]`

`.orange[text]`

`.yellow[text]`

`.green[text]`

`.blue[text]`

`.purple[text]`

`.black[text]`
]
.rightcol45[
**.red[text]**

**.orange[text]**

**.yellow[text]**

**.green[text]**

**.blue[text]**

**.purple[text]**

**.black[text]**
]

---

## .center[Three equal columns]

.cols3[
## Left

Some text
]
.cols3[
## Middle

Some text
]
.cols3[
## Right

Some text
]

---

## .center[Two equal columns]

.leftcol[
## Left side

Some text
]
.rightcol[
## Right side

Some text
]


---
class: center, middle, inverse, no-slide-number

# Thanks!
